\name: A hierarchical Bayesian model for Supernova Cosmology

### 2018-02-28 papers/methods/paper.tex
Reorgansing
Three-ear to three-year

@@

\begin{table}
	\centering
	\caption{Parameter Correlations with $w$ for the combined 100 simulation fits. Correlations for the LowZ band systematics and the latent parameters representing selection function uncertainty are not shown but have negligible correlation.}
	\label{tab:parameter_correlations}
	\begin{tabular}{c|cc}
		Parameter & {\gten} Stat+Syst & {\celeven} Stat+Syst  \\
		\hline
		$\Omega_m$ &   -0.19 &     -0.21     \\
		$\alpha$ &   -0.17 &     -0.20     \\
		$\beta$ &   -0.29 &     -0.23     \\
		$\langle M_B \rangle$ &    0.68 &      0.66     \\
		$\sigma_{\rm m_B}^{0}$ &    0.04 &      0.07     \\
		$\sigma_{\rm m_B}^{1}$ &    0.23 &      0.18     \\
		$\sigma_{x_1}^{0}$ &    0.04 &      0.03     \\
		$\sigma_{x_1}^{1}$ &    0.05 &      0.01     \\
		$\sigma_{c}^{0}$ &    0.01 &      0.11     \\
		$\sigma_{c}^{1}$ &    0.08 &      0.04     \\
		$\alpha_c^{0}$ &   -0.04 &      0.04     \\
		$\alpha_c^{1}$ &    0.03 &      0.01     \\
		$\kappa_{c0}^{0}$ &   -0.10 &     -0.05     \\
		$\kappa_{c0}^{1}$ &   -0.20 &     -0.17     \\
		$\kappa_{c1}^{0}$ &   -0.05 &     -0.01     \\
		$\kappa_{c1}^{1}$ &   -0.01 &      0.01     \\
		$s_c^{0}$ &    0.00 &      0.01     \\
		$\delta(0)$ &    0.00 &      0.00     \\
		$\delta(\infty)/\delta(0)$ &    0.00 &      0.00     \\
		$\langle x_1^{0} \rangle$ &   -0.01 &     -0.05     \\
		$\langle x_1^{1} \rangle$ &   -0.02 &      0.02     \\
		$\langle x_1^{2} \rangle$ &   -0.04 &     -0.04     \\
		$\langle x_1^{3} \rangle$ &   -0.03 &     -0.06     \\
		$\langle x_1^{4} \rangle$ &   -0.06 &     -0.06     \\
		$\langle x_1^{5} \rangle$ &    0.04 &      0.02     \\
		$\langle x_1^{6} \rangle$ &    0.04 &      0.04     \\
		$\langle x_1^{7} \rangle$ &    0.08 &      0.03     \\
		$\langle c^{0} \rangle$ &   -0.05 &     -0.12     \\
		$\langle c^{1} \rangle$ &    0.11 &      0.03     \\
		$\langle c^{2} \rangle$ &    0.11 &      0.06     \\
		$\langle c^{3} \rangle$ &    0.14 &      0.04     \\
		$\langle c^{4} \rangle$ &   -0.11 &     -0.11     \\
		$\langle c^{5} \rangle$ &   -0.15 &     -0.08     \\
		$\langle c^{6} \rangle$ &   -0.12 &     -0.13     \\
		$\langle c^{7} \rangle$ &   -0.12 &     -0.06     \\
		$\delta [ {\rm SALT}_0 ]$ &    0.05 &      0.05     \\
		$\delta [ {\rm SALT}_1 ]$ &   -0.01 &      0.02     \\
		$\delta [ {\rm SALT}_2 ]$ &   -0.10 &     -0.09     \\
		$\delta [ {\rm SALT}_3 ]$ &   -0.03 &     -0.03     \\
		$\delta [ {\rm SALT}_4 ]$ &    0.08 &      0.09     \\
		$\delta [ {\rm SALT}_5 ]$ &    0.01 &      0.02     \\
		$\delta [ {\rm SALT}_6 ]$ &    0.05 &      0.07     \\
		$\delta [ {\rm SALT}_7 ]$ &   -0.11 &     -0.10     \\
		$\delta [ {\rm SALT}_8 ]$ &    0.01 &      0.02     \\
		$\delta [ {\rm SALT}_9 ]$ &    0.02 &      0.02     \\
		$\delta [ {\rm MWE}_{B-V} ]$ &    0.03 &      0.02     \\
		$\delta [ {\rm HST Calib} ]$ &   -0.07 &     -0.07     \\
		$\delta [ v_{\rm pec} ]$ &    0.00 &     -0.01     \\
		$\delta [ {\rm \delta z } ]$ &    0.01 &      0.00     \\
		$\delta [ \Delta g ]$ &    0.05 &      0.11     \\
		$\delta [ \Delta r ]$ &    0.16 &      0.10     \\
		$\delta [ \Delta i ]$ &   -0.16 &     -0.18     \\
		$\delta [ \Delta z ]$ &   -0.26 &     -0.26     \\
		$\delta [ \Delta \lambda_g ]$ &    0.16 &      0.20     \\
		$\delta [ \Delta \lambda_r ]$ &    0.05 &      0.06     \\
		$\delta [ \Delta \lambda_i ]$ &    0.00 &     -0.01     \\
		$\delta [ \Delta \lambda_z ]$ &    0.09 &      0.07     \\
		\hline
	\end{tabular}
\end{table}
%		$\delta [ \Delta t ]$ &   -0.01 &      0.00     \\
%		$\delta [ \Delta y ]$ &   -0.03 &     -0.04     \\
%		$\delta [ \Delta Z ]$ &    0.10 &      0.10     \\
%		$\delta [ \Delta A ]$ &    0.00 &      0.00     \\
%		$\delta [ \Delta u ]$ &   -0.04 &     -0.03     \\
%		$\delta [ \Delta v ]$ &    0.01 &      0.02     \\
%		$\delta [ \Delta \lambda_{t} ]$ &    0.00 &      0.02     \\
%		$\delta [ \Delta \lambda_{y} ]$ &    0.00 &      0.00     \\
%		$\delta [ \Delta \lambda_{z} ]$ &   -0.05 &     -0.04     \\
%		$\delta [ \Delta \lambda_{A} ]$ &    0.00 &     -0.01     \\
%		$\delta [ \Delta \lambda_{u} ]$ &   -0.02 &     -0.02     \\
%		$\delta [ \Delta \lambda_{v} ]$ &   -0.01 &      0.01     \\
%		$\delta [ \Delta gl ]$ &   -0.12 &     -0.13     \\
%		$\delta [ \Delta hm ]$ &    0.02 &      0.01     \\
%		$\delta [ \Delta in ]$ &    0.08 &      0.13     \\
%		$\delta [ \Delta jo ]$ &    0.00 &     -0.01     \\
%		$\delta [ \Delta \lambda_{gl} ]$ &    0.00 &      0.00     \\
%		$\delta [ \Delta \lambda_{hm} ]$ &   -0.01 &     -0.03     \\
%		$\delta [ \Delta \lambda_{in} ]$ &   -0.10 &     -0.12     \\
%		$\delta [ \Delta \lambda_{jo} ]$ &    0.00 &      0.00     \\
%		$\delta [ \Delta p ]$ &   -0.01 &     -0.01     \\
%		$\delta [ \Delta q ]$ &    0.00 &      0.00     \\
%		$\delta [ \Delta R ]$ &    0.00 &      0.01     \\
%		$\delta [ \Delta s ]$ &    0.00 &     -0.01     \\
%		$\delta [ \Delta \lambda_{p} ]$ &    0.00 &      0.01     \\
%		$\delta [ \Delta \lambda_{q} ]$ &    0.01 &     -0.01     \\
%		$\delta [ \Delta \lambda_{r} ]$ &   -0.01 &     -0.01     \\
%		$\delta [ \Delta \lambda_{s} ]$ &    0.00 &      0.00     \\
%		$\delta [ \Delta b ]$ &    0.00 &     -0.01     \\
%		$\delta [ \Delta c ]$ &    0.00 &      0.00     \\
%		$\delta [ \Delta d ]$ &    0.00 &      0.01     \\
%		$\delta [ \Delta e ]$ &    0.00 &      0.00     \\
%		$\delta [ \Delta \lambda_{b} ]$ &    0.00 &     -0.01     \\
%		$\delta [ \Delta \lambda_{c} ]$ &    0.00 &      0.00     \\
%		$\delta [ \Delta \lambda_{d} ]$ &    0.00 &     -0.01     \\
%		$\delta [ \Delta \lambda_{e} ]$ &    0.00 &     -0.01     \\
%		$\Delta_{0}$ &    0.00 &      0.01     \\
%		$\Delta_{1}$ &    0.00 &     -0.01     \\
%		$\Delta_{2}$ &    0.00 &      0.00     \\
%		$\Delta_{3}$ &   -0.01 &     -0.01     \\
%		$\Delta_{4}$ &    0.00 &     -0.01     \\
%		$\Delta_{5}$ &    0.00 &     -0.01     \\
%		$\Delta_{6}$ &    0.00 &      0.00     \\
%		$\Delta_{7}$ &    0.00 &     -0.01     \\

@@

With our model being validated against hundreds of simulation realisations, representing a combined dataset over more than $250\,000$ simulated supernovae, we have been able to accurately determine biases in our model and trace their origin. With the current biases being sub-dominant to the total uncertainty, we now prepare to analyse the DES three-ear dataset. But that, my friends, is another paper.

>>>>

\begin{table}
	\centering
	\caption{Parameter Correlations with $w$ for the combined 100 simulation fits. Correlations for the LowZ band systematics and the latent parameters representing selection function uncertainty are not shown but have negligible correlation.}
	\label{tab:parameter_correlations}
	\begin{tabular}{c|cc}
		Parameter & {\gten} Stat+Syst & {\celeven} Stat+Syst  \\
		\hline
		$\Omega_m$ &   -0.19 &     -0.21     \\
		$\alpha$ &   -0.17 &     -0.20     \\
		$\beta$ &   -0.29 &     -0.23     \\
		$\langle M_B \rangle$ &    0.68 &      0.66     \\
		$\sigma_{\rm m_B}^{0}$ &    0.04 &      0.07     \\
		$\sigma_{\rm m_B}^{1}$ &    0.23 &      0.18     \\
		$\sigma_{x_1}^{0}$ &    0.04 &      0.03     \\
		$\sigma_{x_1}^{1}$ &    0.05 &      0.01     \\
		$\sigma_{c}^{0}$ &    0.01 &      0.11     \\
		$\sigma_{c}^{1}$ &    0.08 &      0.04     \\
		$\alpha_c^{0}$ &   -0.04 &      0.04     \\
		$\alpha_c^{1}$ &    0.03 &      0.01     \\
		$\kappa_{c0}^{0}$ &   -0.10 &     -0.05     \\
		$\kappa_{c0}^{1}$ &   -0.20 &     -0.17     \\
		$\kappa_{c1}^{0}$ &   -0.05 &     -0.01     \\
		$\kappa_{c1}^{1}$ &   -0.01 &      0.01     \\
		$s_c^{0}$ &    0.00 &      0.01     \\
		$\delta(0)$ &    0.00 &      0.00     \\
		$\delta(\infty)/\delta(0)$ &    0.00 &      0.00     \\
		$\langle x_1^{0} \rangle$ &   -0.01 &     -0.05     \\
		$\langle x_1^{1} \rangle$ &   -0.02 &      0.02     \\
		$\langle x_1^{2} \rangle$ &   -0.04 &     -0.04     \\
		$\langle x_1^{3} \rangle$ &   -0.03 &     -0.06     \\
		$\langle x_1^{4} \rangle$ &   -0.06 &     -0.06     \\
		$\langle x_1^{5} \rangle$ &    0.04 &      0.02     \\
		$\langle x_1^{6} \rangle$ &    0.04 &      0.04     \\
		$\langle x_1^{7} \rangle$ &    0.08 &      0.03     \\
		$\langle c^{0} \rangle$ &   -0.05 &     -0.12     \\
		$\langle c^{1} \rangle$ &    0.11 &      0.03     \\
		$\langle c^{2} \rangle$ &    0.11 &      0.06     \\
		$\langle c^{3} \rangle$ &    0.14 &      0.04     \\
		$\langle c^{4} \rangle$ &   -0.11 &     -0.11     \\
		$\langle c^{5} \rangle$ &   -0.15 &     -0.08     \\
		$\langle c^{6} \rangle$ &   -0.12 &     -0.13     \\
		$\langle c^{7} \rangle$ &   -0.12 &     -0.06     \\
		$\delta [ {\rm SALT}_0 ]$ &    0.05 &      0.05     \\
		$\delta [ {\rm SALT}_1 ]$ &   -0.01 &      0.02     \\
		$\delta [ {\rm SALT}_2 ]$ &   -0.10 &     -0.09     \\
		$\delta [ {\rm SALT}_3 ]$ &   -0.03 &     -0.03     \\
		$\delta [ {\rm SALT}_4 ]$ &    0.08 &      0.09     \\
		$\delta [ {\rm SALT}_5 ]$ &    0.01 &      0.02     \\
		$\delta [ {\rm SALT}_6 ]$ &    0.05 &      0.07     \\
		$\delta [ {\rm SALT}_7 ]$ &   -0.11 &     -0.10     \\
		$\delta [ {\rm SALT}_8 ]$ &    0.01 &      0.02     \\
		$\delta [ {\rm SALT}_9 ]$ &    0.02 &      0.02     \\
		$\delta [ {\rm MWE}_{B-V} ]$ &    0.03 &      0.02     \\
		$\delta [ {\rm HST Calib} ]$ &   -0.07 &     -0.07     \\
		$\delta [ v_{\rm pec} ]$ &    0.00 &     -0.01     \\
		$\delta [ {\rm \delta z } ]$ &    0.01 &      0.00     \\
		$\delta [ \Delta g ]$ &    0.05 &      0.11     \\
		$\delta [ \Delta r ]$ &    0.16 &      0.10     \\
		$\delta [ \Delta i ]$ &   -0.16 &     -0.18     \\
		$\delta [ \Delta z ]$ &   -0.26 &     -0.26     \\
		$\delta [ \Delta \lambda_g ]$ &    0.16 &      0.20     \\
		$\delta [ \Delta \lambda_r ]$ &    0.05 &      0.06     \\
		$\delta [ \Delta \lambda_i ]$ &    0.00 &     -0.01     \\
		$\delta [ \Delta \lambda_z ]$ &    0.09 &      0.07     \\
		\hline
	\end{tabular}
\end{table}

@@

%		$\delta [ \Delta t ]$ &   -0.01 &      0.00     \\
%		$\delta [ \Delta y ]$ &   -0.03 &     -0.04     \\
%		$\delta [ \Delta Z ]$ &    0.10 &      0.10     \\
%		$\delta [ \Delta A ]$ &    0.00 &      0.00     \\
%		$\delta [ \Delta u ]$ &   -0.04 &     -0.03     \\
%		$\delta [ \Delta v ]$ &    0.01 &      0.02     \\
%		$\delta [ \Delta \lambda_{t} ]$ &    0.00 &      0.02     \\
%		$\delta [ \Delta \lambda_{y} ]$ &    0.00 &      0.00     \\
%		$\delta [ \Delta \lambda_{z} ]$ &   -0.05 &     -0.04     \\
%		$\delta [ \Delta \lambda_{A} ]$ &    0.00 &     -0.01     \\
%		$\delta [ \Delta \lambda_{u} ]$ &   -0.02 &     -0.02     \\
%		$\delta [ \Delta \lambda_{v} ]$ &   -0.01 &      0.01     \\
%		$\delta [ \Delta gl ]$ &   -0.12 &     -0.13     \\
%		$\delta [ \Delta hm ]$ &    0.02 &      0.01     \\
%		$\delta [ \Delta in ]$ &    0.08 &      0.13     \\
%		$\delta [ \Delta jo ]$ &    0.00 &     -0.01     \\
%		$\delta [ \Delta \lambda_{gl} ]$ &    0.00 &      0.00     \\
%		$\delta [ \Delta \lambda_{hm} ]$ &   -0.01 &     -0.03     \\
%		$\delta [ \Delta \lambda_{in} ]$ &   -0.10 &     -0.12     \\
%		$\delta [ \Delta \lambda_{jo} ]$ &    0.00 &      0.00     \\
%		$\delta [ \Delta p ]$ &   -0.01 &     -0.01     \\
%		$\delta [ \Delta q ]$ &    0.00 &      0.00     \\
%		$\delta [ \Delta R ]$ &    0.00 &      0.01     \\
%		$\delta [ \Delta s ]$ &    0.00 &     -0.01     \\
%		$\delta [ \Delta \lambda_{p} ]$ &    0.00 &      0.01     \\
%		$\delta [ \Delta \lambda_{q} ]$ &    0.01 &     -0.01     \\
%		$\delta [ \Delta \lambda_{r} ]$ &   -0.01 &     -0.01     \\
%		$\delta [ \Delta \lambda_{s} ]$ &    0.00 &      0.00     \\
%		$\delta [ \Delta b ]$ &    0.00 &     -0.01     \\
%		$\delta [ \Delta c ]$ &    0.00 &      0.00     \\
%		$\delta [ \Delta d ]$ &    0.00 &      0.01     \\
%		$\delta [ \Delta e ]$ &    0.00 &      0.00     \\
%		$\delta [ \Delta \lambda_{b} ]$ &    0.00 &     -0.01     \\
%		$\delta [ \Delta \lambda_{c} ]$ &    0.00 &      0.00     \\
%		$\delta [ \Delta \lambda_{d} ]$ &    0.00 &     -0.01     \\
%		$\delta [ \Delta \lambda_{e} ]$ &    0.00 &     -0.01     \\
%		$\Delta_{0}$ &    0.00 &      0.01     \\
%		$\Delta_{1}$ &    0.00 &     -0.01     \\
%		$\Delta_{2}$ &    0.00 &      0.00     \\
%		$\Delta_{3}$ &   -0.01 &     -0.01     \\
%		$\Delta_{4}$ &    0.00 &     -0.01     \\
%		$\Delta_{5}$ &    0.00 &     -0.01     \\
%		$\Delta_{6}$ &    0.00 &      0.00     \\
%		$\Delta_{7}$ &    0.00 &     -0.01     \\

@@

With our model being validated against hundreds of simulation realisations, representing a combined dataset over more than $250\,000$ simulated supernovae, we have been able to accurately determine biases in our model and trace their origin. With the current biases being sub-dominant to the total uncertainty, we now prepare to analyse the DES three-year dataset. But that, my friends, is another paper.
